---
title: "R-egex Assignment"
output: pdf_document
---
# Project Info
**February 2, 2022**  
**Diego Sancho Kruppa 20101377**   
**DSanchoKruppa on GitHub**  
**https://github.com/DSanchoKruppa/R-egexAssignment**  
  
This project demonstrates some dplyr and regex functionality using the 
"measurements.csv" file created for the week 1 assignment. It first shortens
organism genus names to their first initial, then creates a new data.frame
with the original organism column replaced and finally writes it to a .csv.  
  
___
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Set up

```{r, warning=FALSE, message=FALSE}
library(tidyverse)
MData <- read.csv("measurements.csv")
```

## dplyr and regex

```{r}
# finds and replaces the first word in each organism name and replaces it with
# its first letter
MData <- MData %>%
  mutate(Sp = sub("(\\w)\\w+", "\\1.", Organism))

# creates a new dataframe with newly-created Sp replacing Organism as the first
# column
newData <- MData %>% 
  select(Sp, Limb.width, Limb.length, Observer)

# Writing the new dataframe to a .csv
write.csv(newData, "./MeasShort.csv")
```

